---
title: "Exercise 5"
author: "Jai Broome"
date: "May 21, 2016"
output: 
    html_document:
        toc: true
        number_sections: true
---


```{r dependencies, message = FALSE}
require(ggplot2)
```
The `.mat` files have already been read in and saved as `.csv`s since Knitr doesn't play nice with `R.matlab`.
```{r read-data}
train <- read.csv("../data/ex5train.csv")
val <- read.csv("../data/ex5val.csv")
test <- read.csv("../data/ex5test.csv")
```

# Regularized Linear Regression

## Visualizing the dataset
```{r viz-train}
g1 <- ggplot(data = train, aes(X, y)) +
    geom_point(shape = 4, color = "red", size = 3) +
    labs(title = "Figure 1: Training Data", 
         x = "Change in water level (X)", 
         y = "Water flowing out of the dam (y)")
g1
```

## Regularized linear regression cost function
```{r ex1_chunks}
knitr::read_chunk('../ex1/ex1_chunks.R')
```
```{r lin-reg-cost-func}
```

```{r gradient-check}
theta <- c(1,1)
X <- cbind(1, train$X)
y <- train$y
computeCost(X, y, theta)
```

## Fitting linear regression
```{r ex5_chunks}
knitr::read_chunk('ex5_chunks.R')
```

```{r trainLinearReg}
```

```{r optim}
learnedTheta <- trainLinearReg(X, y)
```

```{r plot-learnedTheta}
g1 + geom_abline(slope = learnedTheta$par[2], intercept = learnedTheta$par[1])

lm(y ~ X + 1, train)$coefficients
learnedTheta$par
```

`learnedTheta` matches the coefficients from `R`'s built-in linear regression function

# Bias-variance
Note that the lambda is passed as a parameter to the `learningCurve` function.

When you are computing the training set error, make sure you compute it on the training subset (i.e., X(1:n,:) and y(1:n)) (instead of the entire training set). However, for the cross validation error, you should compute it over the entire cross validation set. You should store the computed errors in the vectors error\_train and error\_val.

## Learning curves
```{r learningCurve}
```
```{r plot-learning-curves}
errors <- learningCurve(X, y, cbind(1, val$X), val$y)
g2 <- plotLearningCurve(errors)
g2
```

# Polynomial regression
```{r polyFeatures}
```

## Learning Polynomial Regression

```{r featureNormalize}
```
```{r polyPlots}
```

```{r}
polyPlots(train$X, train$y, val$X, val$y, n = 12, lambda = 0, p = 8)
```